Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-08-30 analysis/presentation/sim_survey_presentation.Rmd
Add another true vs est plotting option using crosstalk::filter_select

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      fig.width = 10, 
                      fig.height = 5)
knitr::opts_knit$set(root.dir = "../..")
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      fig.width = 10, 
                      fig.height = 5.2)
knitr::opts_knit$set(root.dir = "../..")
```

@@

## Age strat

### Some results

<dev class = "left">
```{r}
plot_age_strat_fan(sim, surveys = 1:5, 
                   plot_bgcolor = "transparent",
                   paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>
